The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-05-30 manuscript/5pillars.Rmd
#6 resolved

Although regular software updates are overall a good thing, it poses a problem for future
reproducibility.
A researcher trying to reproduce a ten-year-old study in R v3.0 could have a headache, as they would need
to roll back their R version, and possibly their operating system as well, as R and other languages
require certain system libraries for low-level routines.

@@

The key technological advances enabling the five pillars approach have been around for about a decade,
yet progress on integrating these into computational research publications has been minimal.
Part of the problem is the incentive structures in academia, with funding bodies and journals are
focused on novel research directions rather than confirming previous findings
[@Kaelin2017-id; @Munafo2017-ty].
Indeed the number of systematic replication studies in bioinformatics remains small
(e.g.: [@Ioannidis2009-hv; ; @Samuel2022-ha]), so we don't have much of a grasp as to how severe the
problem actually is.

>>>>

Although regular software updates are overall a good thing, it poses a problem for future
reproducibility.
A researcher trying to reproduce a ten-year-old study in R v3.0 could have a headache, as they would need
to roll back their R version, and possibly their operating system as well, as R and other languages
require certain system dependencies for low-level routines @Vallet2022-no.

@@

The key technological advances enabling the five pillars approach have been around for about a decade,
yet progress on integrating these into computational research publications has been minimal.
Part of the problem is the incentive structures in academia, with funding bodies and journals are
focused on novel research directions rather than confirming previous findings
[@Kaelin2017-id; @Munafo2017-ty; @Diong2021-is].
Indeed the number of systematic replication studies in bioinformatics remains small
(e.g.: [@Ioannidis2009-hv; @Zaringhalam2020-ms; @Samuel2022-ha]), so we don't have much of a grasp as to how severe the
problem actually is.
